Distributed Tic Tac Toe:\\ Peer-to-Peer Team-Based Gaming System

### 2017-12-01 paper/paper.tex
citations fixed

Currently, when running the game, the user supplies a local instance name and the name of another instance as command line arguments. Each instance then uses this information to do an RMI Registry lookup and get a reference to the other client.

>>>>

Currently, when running the game, the user supplies a local instance name and the name of another instance as command line arguments. Each instance then uses this information to do an RMI Registry lookup and get a reference to the other peer to attempt to establish a session. This allows multiple different sessions to run simultaneously on the same network without interference - ideal for educational use, where multiple groups are likely to be working on the same internal network.
